Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-03-12 response_to_review_SOLA-D-20-00015_v1.txt

-----------------------------------------------------------------------------------------
Q2. Figure 3 and 11, bottom panels. I find it difficult to distinguish between the red and magenta colours. Can you replace magenta with a different colour, maybe green?

A2. We agree. Actually this affects all following Figures: 3, 4, 11, and 14. In those, we applied the following changes: Red->Orange and Magenta->Red. These emulate our previous choice of colors in Nuevo et al. (2013) and Lloveras et al. (2017). We like to keep all "up" structures in a "warm" palette. We edited text accordingly all along the manuscript. We believe the colors are now clearly distinguishable in all figures.

-----------------------------------------------------------------------------------------
Q3. Page 14, paragraph starting at line 34. You discuss the latitudinal distribution of short and long loops, and state that the small legs mainly populate the equatorial latitudes, and longer legs at higher latitudes. But this is a skewed result - their spatial positioning was a criteria for their categorisation, so this should not be presented as a scientific result.

A3. Several aspects are involved here, the discussion in the paragraph you indicate strongly relates on that in the final paragraph of Section 2.3. In reading them we find that these texts were confusing as they were, so we edited both. Actually, we do not say that *small* legs populate the equatorial latitudes and *large* ones the mid latitudes. We say that if one classifies the *small-closed* loops in DOWN and UP, the former peak near the equator and the latter peak near mid latitudes (at least for the deep minimum rotation CR-2082). The classification of legs in all four classes in Section 2.3 includes limits for the latitude of their footpoints, to distinguish different layers of the streamer belt (legs of type 0, I and II), as well as to separate field lines of the high latitude CHs (legs of type III). We included two new panels in Figure 3, showing frequency histograms of the latitude of the four types of legs at 1.105 Rsun. Within the range Abs(latitude) < 50 deg, and for the solar minimum target CR-2082, down-legs are peaked near the equator while up-legs peak at mid-latitudes. This is less obvious for CR-2208, although it is clear that down-legs peak in the core of the streamer belt. If one analyses Abs(latitude) > 50 deg it turns out that small-down legs are scarce and there is an extra population of small-up legs (not nearly as much as in the peaks seen at mid lats. Should have we not included the limit of Abs(latitude) < 50 deg for closed-small down and up legs (i.e., legs of type 0 and I), their histograms would still peak at around the same latitudes. This can be seen in Figure 7 of Nuevo et al. 2013), were they analysed the small closed up and down loops for two rotations of solar minimum, without placing any limits in the latitude of the footpoints. As our main objective here is to be able to analyse progressively outer layers of the streamer belt, we include these limits in the latitude of the footpoints. We edited in full the final paragraph of Section 2.3, as well as the paragraph of Section 3.1 you point out (now split in two, shorter paragraphs). We trust the new graphs and discussions are clear now. Let us know.

@@

A4. When selecting field lines for analysis of both the DEMT and the AWSoM models, the classification of types of legs introduced in section 2.3 is applied to the DEMT reconstruction and the AWSoM model separately. As a result, as shown by comparing the middle panels of Figure 3 and the bottom panels of Figure 11, and as discussed in the corresponding texts of the manuscript, the selection of field lines for DEMT is not the same as the selection of field lines for the AWSoM model. In comparing those Figures each color indicates comparable regions between the two analysis. It is so that Figures 12 and 13, and Table 2, which show DEMT-versus-AWSoM comparison for each rotation, are not done line-by-line but rather region-by-region (orange, red and cyan). The suggestion of calculating the MAD would require selecting the same field lines for both models, which is beyond the scope of the present comparative analysis. Informing the MAD is a good idea, being a robust quantitative measure of how the comparison between both models spreads. We will certainly implement such an analysis in a next effort. In the present draft, we trust the current comparison (Figures 12 and 13, and Table 2) provide a pretty informative summary of how both models compare. Let us know what you think.

-----------------------------------------------------------------------------------------
Q5. You discuss the less reliable results from AIA in coronal holes. The very recent paper by Saqri et al (Solar Physics 295, 2020) is relevant here, and should be referenced.

A5. Thanks for the reference, which is certainly relevant and now mentioned in the paper, as discussed below. We are not sure stray light contamination is actually the fundamental reason of the reported issue, which is now solved, as described next.

The discussion section of v1 of the draft includes this sentence (now deleted): "The source of this distinct performance of DEMT when applied to EUVI or AIA data is related to the TRFs of the respective filter sets. We are currently implementing an improved LDEM determination algorithm to deal with this issue that will be used in a follow up article." While waiting for your report and preparing V2 of the draft, we successfully implemented the improved version of the code, as a result of which this problem has been solved. The issue was related to the algorithm that solves the optimization problem posed in each voxel to find the LDEM. When based on AIA data, the previous algorithm tended to converge to a non-optimal (local minimum of the objective function) in specific voxels located in the CHs. We addressed the problem by exploring multiple starting points when solving the optimization problem in cases where the initial solution was not good enough. In this draft, the improved algorithm affects results concerning type III legs for CR2208. As a result, the following Figures have been updated: 2, 3, 4, 5, 10, 13 and 14. You will notice all these Figures are just like the original ones, except in the CHs of CR-2208, where the previous issue has been solved. The text throughout the manuscript was edited accordingly, in the following pages of V2 of the draft:
 - Related text in Pgs. 12-15 (some of the red text in these pages relates to Q4 above).
 - Numerical values concerning legs of type-III for CR-2208 in Tables 1 and 2.
 - Most of the third paragraph of the Conclusion section in V1 was devoted to this issue, so it was eliminated. The remaining text is now the end of the second paragraph of that section (highlighted in red color).

@@

Agreed, removed.

- Section 4, first two paragraphs.

Agreed, removed. We edited the new first paragraph in this section (red text) following also your suggestions in Q10 below, although we wanted to keep references to specific Figures and Tables here.

- Page 26, line 26:
 'In the streamer belt region we combined the DEMT results and the AWSoM magnetic model to infer the energy input phi at the coronal base required to maintain stable coronal loops. We found characteristic values in the range…'
Shorten to: 'The energy input phi at the coronal base, required to maintain stable coronal loops, is in the range…'

### 2020-03-12 lloveras_2020_v2.tex
version distribuida a los colaboradores con las correcciones del referi

{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, \textit{i.e.} $E_c(s)=[1/A(s)]\,{\rm d}[A(s)\,F_c(s)]/{\rm d}s$, where $A(s)$ is the transverse area of the magnetic flux tube at position $s$. Under a quiescent solar corona plasma regime, the conductive flux is assumed to be dominated by the electron thermal conduction, described by the usual Spitzer model \citep{spitzer_1962}

>>>>

{The thermal conduction power $E_c$ equals the divergence of the conductive heat flux $F_c$, \textit{i.e.} $E_c(s)=[1/A(s)]\,{\rm d}[A(s)\,F_c(s)]/{\rm d}s$, where $A(s)$ is the \edit{cross-sectional} area of the magnetic flux tube at position $s$. Under a quiescent solar corona plasma regime, the conductive flux is assumed to be dominated by the electron thermal conduction, described by the usual Spitzer model \citep{spitzer_1962}
